\documentclass[11pt, letterpaper]{moderncv}

\usepackage{ifthen}

\ifthenelse{\equal{\detokenize{english}}{\jobname}}{
    \newcommand{\de}[1]{}
    \newcommand{\en}[1]{#1}
}{
    \newcommand{\de}[1]{#1}
    \newcommand{\en}[1]{}
}

\en{\usepackage[english]{babel}}
\de{\usepackage[ngerman]{babel}}

\usepackage[utf8]{inputenc}
\usepackage[left=1.7cm, right=1.7cm, top=1.0cm, bottom=1.0cm, scale=0.8]{geometry}
%\usepackage{fontawesome}

% source: https://tex.stackexchange.com/a/294990/271172
\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }
\renewcommand{\link}[2]{\href{#1}{#2 \ExternalLink}}


\newcommand{\quotes}[1]{\en{``#1''}\de{\glqq{}#1\grqq{}}}
\renewcommand*{\namefont}{\fontsize{20}{22}\mdseries\upshape}

\moderncvtheme[blue]{classic}
\moderncvicons{awesome}
 
\name{Johannes}{Esslinger}
\title{\en{Resume}\de{Lebenslauf}}
% \address{}{}
% \phone[mobile]{}
\email{johannesesslinger@gmail.com}
%\social[github][https://github.com/JohannesEsslinger]{Johannes Esslinger}
\social[linkedin][https://www.linkedin.com/in/johannes-esslinger-0b5197211/]{Johannes Esslinger}
% \photo[2.5cm]{images/photo}
 
\begin{document}
\vspace*{-10mm}
\makecvtitle
\vspace*{-13mm}

\section{\en{Objective}\de{Persönliche Daten}}
\cvline{\en{}\de{geboren}}{\en{
    Seeking a challenging machine learning internship to apply my strong mathematical and programming skills to new, unexplored 
    challenges in the field. My enduring enthusiasm, cultivated at an early age exploring my father's C-language books, is a vital 
    asset poised to drive innovation and benefit your company.
} \de{09.10.1998, Bad Mergentheim}}


\section{\en{Experience}\de{Berufserfahrung}}
\cventry{08.2023-\en{current}\de{heute}}
        {\en{Research Assistant}\de{Wissenschaftlicher Mitarbeiter}}
        {\en{Autonomous Learning Robots (ALR) Lab at KIT}\de{Autonome Lernende Roboter (ALR) am KIT}}
        {}
        {}
        {\en{
        \begin{itemize}
            \item Currently involved in an ongoing extensive benchmarking study to evaluate state-of-the-art Variational Inference methods.
            \item Obtaining experience with machine learning models implemented in JAX within a scientific setting, which allows me to deepen my understanding of various mathematical concepts.
        \end{itemize}}
        \de{
        \begin{itemize}
            \item Derzeit beteiligt an einer umfassenden Benchmarking-Studie zur Bewertung modernster Techniken Variational Inference. 
        \end{itemize}}
        }
\cventry{10.2022-07.2023}
        {\en{Working Student}\de{Werkstudent}}
        {EnBW Energie Baden-Württemberg AG}
        {}
        {}
        {\en{
        \begin{itemize}
            \item Conducted data validation and reconciliation tasks, utilizing SQL queries as part of the process to develop a data warehouse on the Snowflake platform.
            \item Actively participated in the development and scaling of automation bots with UIPath, enhancing process efficiency through a significant reduction in workforce requirements.
            \item Designed and constructed operational dashboards for process monitoring, utilizing DataDog to provide real-time insights and visibility into critical business operations.
        \end{itemize}}
        \de{
        \begin{itemize}
            \item Durchführung von Datenvalidierungs- und Abgleichsaufgaben unter Verwendung von SQL-Abfragen als Teil des Prozesses zur Entwicklung eines Data Warehouse auf der Snowflake-Plattform.
            \item Aktive Beteiligung an der Entwicklung und Skalierung von Automatisierungsrobotern mit UIPath zur Verbesserung der Prozesseffizienz und Workflow-Automatisierung.
            \item Entwicklung und Erstellung von operativen Dashboards für die Prozessüberwachung unter Verwendung von DataDog, um Echtzeiteinblicke und Einblicke in kritische Geschäftsvorgänge zu ermöglichen.
        \end{itemize}}
        }
\cventry{05.2022-10.2022}
        {\en{Software Engineering Internship}\de{Praktikum}}
        {Georg Schumann GmbH \& Co. KG}
        {}
        {}
        {\en{
        \begin{itemize}
            \item Conceived, planned, executed, and deployed an automated system for optimizing joinery operations, leveraging .NET framework and C\# programming.
            \item Gained expertise in software engineering, with a strong emphasis on parallel programming, to facilitate correct inter-process communication.
            \item Showed strong endurance communication, and collaboration skills by working with various stakeholders to ensure the project's success despite encountering numerous bugs in the provided joinery machine's dll.
        \end{itemize}}
        \de{
        \begin{itemize}
            \item Konzeption, Planung, Ausführung und Einsatz eines automatisierten Systems zur Optimierung von Abbundarbeiten unter Verwendung von .NET Framework und C\#-Programmierung
            \item Erlangung von Fachkenntnissen in der Softwareentwicklung mit Schwerpunkt auf paralleler Programmierung.
            \item Demonstration von Hartnäckigkeit, effektiver Kommunikations- und Kooperationsfähigkeiten durch die Zusammenarbeit mit verschiedenen Interessengruppen, um den Erfolg des Projekts zu gewährleisten.
        \end{itemize}}
        }
\cventry{04.2021-02.2022}
        {\en{Working Student}\de{Werkstudent}}
        {\en{Vector Informatik GmbH}\de{Vector Informatik GmbH}}
        {}
        {}
        {\en{
        \begin{itemize}%
            \item Developed and implemented consistency rules using Java-based utility methods to guarantee compliance with established guidelines in PREEvision.
            %\item Created an automated reporting system to enhance project documentation and traceability, acquiring hands-on proficiency in Java.
            \item Contributed to the development and execution of test cases using JUnit, thereby enhancing product quality and reliability.
        \end{itemize}}
        \de{
        \begin{itemize}
            \item Entwicklung von Konsistenzregeln unter Verwendung von Java-basierten Dienstprogrammen, um die Einhaltung der festgelegten Richtlinien in der modellbasierten Entwicklungsumgebung PREEvision zu gewährleisten.
            %\item Erstellung und Pflege eines umfassenden Berichts zur Darstellung von Anforderungen in PREEvision zur Verbesserung der Projektdokumentation und Rückverfolgbarkeit.
            \item Mitwirkung an der Entwicklung und Ausführung von Testfällen unter Verwendung von JUnit zur Verbesserung der Produktqualität und Zuverlässigkeit.
        \end{itemize}}
        }

\section{\en{Education}\de{Ausbildung}}
\cventry{2022-\en{today}\de{heute}}
        {\en{Karlsruhe Institute of Technology (KIT)}\de{Karlsruher Institut für Technologie (KIT)}}
        {M.Sc. \en{Computer Science}\de{Informatik}}
        {}
        {}
        {\en{GPA: 3.7/4.0 (Current)}\de{Durchschnittsnote: 1,3}\\
        \en{Minor: Mathematics}\de{Nebenfach: Mathematik}}
\cventry{2018-2022}
        {\en{Karlsruhe Institute of Technology (KIT)}\de{Karlsruher Institut für Technologie (KIT)}}
        {B.Sc. \en{Computer Science}\de{Informatik}}
        {}
        {}
        {\en{GPA: 3.1/4.0}\de{Durchschnittsnote: 1,9}\\
        Thesis:
        \en{\quotes{Evaluation of Deep Learning Methods for Real Time Object Detection of Bulk Materials at Different Occupancy Densities}}
        \de{\quotes{Evaluation von Deep Learning Verfahren zur echtzeitfähigen Objektdetektion von Schüttgütern bei verschiedenen Belegungsdichten}}\\}

\section{\en{Skills and Languages}\de{Fähigkeiten}}
\cvcomputer{\en{Programming}\de{Programmierung}}{Python, Java, C\#, SQL}{\en{Technologies}\de{Technologien}}{Linux, Jax, PyTorch, Git, .Net-Framework, Snowflake, Pandas}
\cvcomputer{\en{Languages}\de{Sprachen}}{\en{German: Native, English: Fluent}\de{Deutsch}}{}{}

%\section{\en{Languages}\de{Sprachen}}
% use \cvcomputer for multi column descriptions
%\cvcomputer{\en{German}\de{Deutsch}}{\en{Native}\de{Muttersprache}}
%           {\en{English}\de{Englisch}}{\en{Fluent}\de{Fließend}}



\section{\en{References}\de{Referenzen}}
\cvline{\en{}\de{}}{\en{References available upon request} \de{Referenzen auf Anfrage erhältlich}}

\emptysection{}\closesection
\vfill
{\de{Johannes Esslinger\\
Karlsruhe, \today}}
\end{document}